The Accuracy of KNN, decision tree, random forest, SVM, neural network, naive Bayes classifier and PLA for early Prediction of Diabetes

### 2023-04-05 hw1/paper/main.tex

After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.
\section{Naive Bayes classifier}

>>>>

  After the end of the iteration, multiply $T$ by $R_T$ and continue the iteration until the $T \le T_E$.Then, we get the approximate 
  solution$f=f^*$.Every 2 iteration, the $T$ decreases and lower the probability of $f^{**}$ accepted as the solution.Stimulating annealing 
  can avoid solution stuck at local minimum.Use neural network found by NAS, we can now predict with untrained data with $80\%$ or so accuracy.

\section{Naive Bayes classifier}
  First, let's explain the princple of Naive Bayes classifier, here is a very intuitive and easy-to-understand example, consider 
  you are a scientist who study earthquake, what a intresting relation attract you is when there are eqrthquake, the number of 
  rainy days is particular high while its low when there are no earthquake. Although it may sounds nonsense, we can assume there 
  may exists a positive relation betweeen earthquake and rainy days. Here we talk about the Bayesian theorem, which is the basis 
  of naive Bayes classifier. What the formula it give is $P(A|B) = \frac{P(A\capB)}{P(B)}$. Consider we need to predict the result 
  by the data meaning the outcome will be unknown, what we need do is just change the formula a little bit and it becomes: $P(A|B) = \frac{P(B|A)*P(A)}{P(B)}$. 
  We can consider $A$ as the outcome and $B$ as data. Given a data that contains a sequence of data and various outcomes. We just 
  record each event in each dimension and compute their conditional probabilities for each outcome and store these result in other 
  place. When predicting the outcome using given data, find the conditional probability of each event in given data for one outcome 
  and multiply them. Keep repeating until we had computed all conditional probability for each outcome, then find the maximum one, 
  which is the most likely outcome. The problem is, when given is a continuous value instead of individual events, it look like we 
  need to partition this continuous interval as individual events. However, the difficulty is how to find the best partition that 
  can fit the model best. What I use to slove this problem is gene alogrithm. First ecord maximum and minimum values of given data 
  in each dimension. Step2 is randomly partition data in each dimension according the maximum and minimum value we record before 
  and repeat 100 times to generate enoguh species. Step3 is test the accuracy of the model on the training data and keep top 15 
  good species and kill the rest. Step4 is let the these elite to crossover, which means let them pass their partition to kids. 
  Step4 is when there is enough offspring, all offspring will start mutation, which means their partitions will slightly shift, 
  merge, split, or disapar etc..., make each animal different to optmize the model. And back to step2, here I called an evolution. 
  We thus find the partition that is close to optimal solution after enough evolution.
